---
title: "Assignment4-Group3"
author: "Group3"
date: "03/06/2020"
output:
  bookdown::html_document2
---


```{r echo = FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

# Ketan Kabu:

## Correlation of version development and rating

### What is version code?

Version code is a positive integer used as an internal version number. This number is used only to determine whether one version is more recent than another, with higher numbers indicating more recent versions. The value is a positive integer so that other apps can programmatically evaluate it, for example to check an upgrade or downgrade relationship.@mcmurtry_zampano_2020

```{r}
library(tidyverse)
library(dplyr)
library(kableExtra)
library(plotly)
```


```{r}
# Reading the data
data <- read.csv(here::here("data", "AppleStore.csv"))

```


```{r}
vers <- data %>% 
  filter(!rating_count_tot %in% 0:99) %>% 
  mutate(Main_Ver = as.integer(sub("\\..*", "", ver))) # Removed apps that have total ratings posted less than 100, as this indicates a considerable lack of usage

```
### Average number of app developments of top 30 apps

Top 30 apps are chosen on the basis of usage, which in this case is assumed to be total rating counts.



```{r app-tab}
# Filtering top 30 apps by usage (rating count)
top_apps <- vers %>% 
  arrange(desc(rating_count_tot)) %>% 
  slice(1:30)

# Calculating average major development for top 30 apps  
top_apps_dev <- top_apps %>% 
  group_by(track_name) %>%
  summarise(`Average Major Developments` = as.integer(mean(Main_Ver, na.rm = TRUE))) %>% 
  arrange(desc(`Average Major Developments`)) %>% 
  rename("App" = track_name)

# Creating table using kable to display findings
knitr::kable(top_apps_dev, caption = "Top apps and their developments") %>% 
  kable_styling(latex_options = c("striped", "hold_position"))
```
Table \@ref(tab:app-tab)


Facebook is the app that by far has had the most developments out of the top 30 apps, with 95 major developments. This is followed by Google with 27 and Instagram with 10. 
Interestin to note that Temple Run and Subway Surfers, 2 apps that are widely popular and been around since a long time have only had 1 major development.


## Average number of app developments of all genres

Let's take a look at the genres with highest number of major developments


```{r genre-tab}
genre_dev <- vers %>% 
  group_by(prime_genre) %>% 
  summarise(`Average Developments` = as.integer(mean(Main_Ver, na.rm = TRUE))) %>%   arrange(desc(`Average Developments`)) %>% 
  rename("Genre" = prime_genre)

#Creating table using kable to display findings
knitr::kable(genre_dev, caption = "Genres and their developments") %>% 
  kable_styling(latex_options = c("striped", "hold_position"))
```
Table \@ref(tab:genre-tab)

As we can see, Finance and Sports apps seem to have a massive number of developments with 100 and 34 average major developments respectively. Is it that all Finance and Sports apps have such massive number of developments or are there outliers spiking the average?

### Finance apps with most number of developments
```{r finance-tab}
finance_dev <- vers %>%
  filter(prime_genre == "Finance") %>% 
  group_by(track_name) %>% 
  summarise(`Average Developments` = as.integer(mean(Main_Ver, na.rm = TRUE))) %>%   arrange(desc(`Average Developments`)) %>% 
  rename("Apps" = track_name) 
finance_dev <- finance_dev %>% 
  slice(-c(3,4,12,13,20,22,24,25)) # Removing app names that are not readable
finance_dev <- finance_dev %>% slice(1:20) # Displaying top 20 apps
  
#Creating table using kable to display findings
knitr::kable(finance_dev, caption = "Finance app developments") %>% 
  kable_styling(latex_options = c("striped", "hold_position"))  
  
```
Table \@ref(tab:finance-tab)

Stock Market HD and Stock Market Pro clearly show a much higher number of major developments, 2023 each. The 3rd highest developed app, Citi Mobile, has had only 8 major developments. 

### Sports apps with most number of developments
```{r sports-tab}
sports_dev <- vers %>%
  filter(prime_genre == "Sports") %>% 
  group_by(track_name) %>% 
  summarise(`Average Developments` = as.integer(mean(Main_Ver, na.rm = TRUE))) %>%   arrange(desc(`Average Developments`)) %>% 
  rename("Apps" = track_name) 
sports_dev <- sports_dev %>% slice(-c(15,23)) # Removing app names that are not readable

sports_dev <- sports_dev %>% slice(1:20) # Displaying top 20 apps
  
#Creating table using kable to display findings
knitr::kable(sports_dev, caption = "Sports app developments") %>% 
  kable_styling(latex_options = c("striped", "hold_position"))  
  
```
Table \@ref(tab:sports-tab)

Like finance apps in table \@ref(tab:finance-tab), the app NBA spikes the average developments of the sports genre with 2013 major developments, whereas, the second highest app NFL only has 14 major developments.

### Relationship between major developments and rating

```{r}
# Tidying data before plotting
plot_genre_data <- vers %>%
  select(prime_genre, user_rating, Main_Ver) %>% 
  group_by(prime_genre) %>% 
  summarise(`Average Developments` = as.integer(mean(Main_Ver, na.rm = TRUE)),
            `Average Ratings` = as.numeric(mean(user_rating, na.rm = TRUE))) %>%    arrange(desc(`Average Developments`)) %>%
  rename("Genre" = prime_genre)

plot_genre_data$`Average Ratings` <- round(plot_genre_data$`Average Ratings`, 1)
```

Please hover pointer over the scatter plot points to view the Genre

```{r devplot, fig.align="center", fig.cap="Development-Rating correlation"}
# Plotting
dev_plot <- plot_genre_data %>%
  ggplot(aes(x = `Average Developments`, y = `Average Ratings`, color = Genre)) + 
  geom_point(alpha = 0.7)

ggplotly(dev_plot)
```
Figure \@ref(fig:devplot)


The plot above indicates that finance apps (on the far right) have had way more major developments than any other genre of apps, but not a relatively high rating.
Most of the app genres lie in the range of 1-12 developments, while also hovering around the 4 star rating, which is quite decent.
But finance and sports, with their huge number of major developments, lie below 4 rating, with sport at 3.6 and finance at 3.8 respectively.

Although, we know from table \@ref(tab:finance-tab) and \@ref(tab:sports-tab) that not all apps in these genres have had that many developments, with only a few spiking the average.

Health And Fitness, Games have the highest average rating among all genres, even though average major developments are only 3 and 4 respectively.

For Finance and Sports, though, if we remove the outliers spiking the average, what would the above plot shape up to be?

```{r}
plot_genre_filt <- vers %>%
  select(prime_genre, track_name, user_rating, Main_Ver) %>% 
  filter(!track_name %in% c("NBA", "Stock Market HD: Real Time Stocks Tracker + Forex", "Stock Market Pro: Stock Trading, Charts & Alerts")) %>% 
  group_by(prime_genre) %>% 
  summarise(`Average Developments` = as.integer(mean(Main_Ver, na.rm = TRUE)),
            `Average Ratings` = as.numeric(mean(user_rating, na.rm = TRUE))) %>%    arrange(desc(`Average Developments`)) %>%
  rename("Genre" = prime_genre)
plot_genre_filt$`Average Ratings` <- round(plot_genre_filt$`Average Ratings`, 1)
```


```{r devplot-filt, fig.align="center", fig.cap="Development-Rating correlation (updated)"}
dev_plot_filt <- plot_genre_filt %>%
  ggplot(aes(x = `Average Developments`, y = `Average Ratings`, color = Genre)) + 
  geom_point(alpha = 0.7)

ggplotly(dev_plot_filt)
```
Figure \@ref(fig:devplot-filt)

By removing only 2 outlier apps (Stock Martket Pro, Stock Markter HD) from Finance and one (NBA) from Sport, the graph becomes much more appropriately scaled. Finance average developments drop from 100 to 4, whereas Sports drops from 34 to 4.
So, in figure \@ref(fig:devplot-filt) we see that Entertainment becomes the most developed genre at average 7 major developments, and even in this case, with an average rating of 3.8, the genre is not nearly one of the best rated. Clearly, app developments isn't corresponding to actually high ratings.


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,  message=FALSE, warning = FALSE)
```

```{r library}
library(tidyverse)
library(readr)
library(kableExtra)
library(ggplot2)
library(forcats)
```

```{r Read data source 1, fig.cap=" ", echo = FALSE, message = FALSE, warning=FALSE}
dat <- read_csvdat <- read_csv(here::here("data/AppleStore.csv"))
```


# Diyao Chen

Nowadays, more and more different type of App on the market. Some is for work, some is for entertainment,we know to know the feekback from the consumers.
In this section, we will analysis the realtionship between different type of app with user rating, language and support different devices.

1. Which genre are highest rated?
```{r q1, fig.cap="Research for gener with rating ", echo = FALSE, message = FALSE, warning=FALSE}
genre_rating <- dat%>%
  group_by(prime_genre)%>%
  summarise(average_rating = mean(user_rating))%>%
  arrange(-average_rating)%>%
  unique()

 knitr::kable(head(genre_rating,10),booktabs = TRUE,
  caption = "Table1. Ranking of rating with different genre") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))%>%
  kable_styling(latex_options = "hold_position") 
  

Graph1<- genre_rating%>%
  ggplot(aes(x =reorder(prime_genre,-average_rating), y = average_rating,fill = prime_genre))+
  geom_bar(stat = "identity", show.legend = FALSE)+
  ggtitle("Figure1. The ranking rate with different genre Apps")+
  theme(axis.text.x=element_text(angle = 90, hjust = 1)) +
  labs(x = "Genre" , y = "Average Rating")
Graph1
```
As we can see from the table1 and the figure1, there are 23 different types of App in the research. The highest rating is type of productivity, which is 4 mark.On the other hand, the lowest rating is catalogs, which is 2.1 mark. overall, the different type of App's ratings are fairly close. The gap of highest and lowest is 1.9.and the top and the second within a tenth of a point.


2. Which genre support most language?
```{r q2, fig.cap="Research for gener with language", echo = FALSE, message = FALSE, warning=FALSE}
gener_language <- dat%>%
  group_by(prime_genre)%>%
  summarise(average_language = mean(lang.num))%>%
  arrange(-average_language)%>%
  unique()


 knitr::kable(head(gener_language,10),booktabs = TRUE,
  caption = "Table2. Ranking of language with different genre") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))%>%
  kable_styling(latex_options = "hold_position") 
   
  

Graph2<- gener_language%>%
  ggplot(aes(x =reorder(prime_genre,-average_language), y = average_language, fill = prime_genre))+
  geom_bar(stat = "identity", show.legend = FALSE)+
  ggtitle("Figure2. The ranking language with different genre Apps")+
  theme(axis.text.x=element_text(angle = 90, hjust = 1)) +
  labs(x = "Genre" , y = "Average Language")
Graph2
```

As we can see from table2 and figure2, the genre of productivity is support the most language, which is the type of 11 different languages.And the lowest is the Finance app, only support 2 types of language about that. The gap is huge between the top and the lowest, but every type of Apps Will provide at least two different languages.

3. Which genre support most devices?
```{r q3, fig.cap="Research for gener with devices", echo = FALSE, message = FALSE, warning=FALSE}
gener_devices <- dat%>%
  group_by(prime_genre)%>%
  summarise(average_devices = mean(sup_devices.num))%>%
  arrange(-average_devices)%>%
  unique()


 knitr::kable(head(gener_devices,10),booktabs = TRUE,
  caption = "Table3.Ranking of support devices with different genre") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))%>%
  kable_styling(latex_options = "hold_position") 
  

Graph3<- gener_devices%>%
  ggplot(aes(x =reorder(prime_genre,-average_devices), y = average_devices, fill = prime_genre))+
  geom_bar(stat = "identity", show.legend = FALSE)+
  ggtitle("Figure3.The ranking devices with different genre Apps")+
  theme(axis.text.x=element_text(angle = 90, hjust = 1)) +
  labs(x = "Genre" , y = "Average Devices")
Graph3
```

As we can see from table3 and figure3,the top on support devices is Games.It support 38 different types of devices and the lowest is Music,which support 35 different types of devices.Each type of app is at least 35 different devices.The gap between the top and lowest is very close.

# Sen Wang


```{r tidy-data}
data2 <- dat %>%
  filter(rating_count_tot > 100) %>%
  mutate(size_mb = size_bytes/1024/1024)
```

1. Genre-rating-price correlation?

```{r data_plot1, fig.cap="No strong relation between app categories and user ratings in different price", message=FALSE, warning=FALSE, fig.width=12, fig.height=12}
# A histogram showing the relation between app categories and user ratings in different price.
data2 %>%
  ggplot(aes(x = prime_genre,
             y = user_rating,
             fill = prime_genre)) +
  geom_histogram(stat = 'summary',
                 fun.y = mean,
                 show.legend = FALSE) +
  coord_flip() +
  labs (x = "Categories", 
        y = "Average of user rating",
        title = "No strong relation between app categories and user ratings in different price") +
  facet_wrap(~price) +
  theme_minimal()
```

According to the Figure \@ref(fig:data_plot1), there is no strong relationship between app categories and user ratings in different price. Each type of App has similar user ratings at different prices. However, we can find that the price of shopping and financial apps is lower than that of other apps, which may be because they hope to gain more users through low threshold, and medical apps are the most expensive, which may be because they provide valuable information about users' health.

2. Genre-rating-size correlation?

```{r data_plot2, fig.cap="The relation between app size and user rating in different genres", message=FALSE, warning=FALSE, fig.width=12, fig.height=12}
# The relation between app size and user_rating in different app categories.
data2 %>%
  ggplot(aes(x = user_rating,
             y = size_mb)) +
  geom_line(stat = 'summary',
            fun.y = mean) +
  labs (x = "Average of user rating",
        y = "Size (MB)",
        title="The relation between app size and user rating in different genres") +
  facet_wrap(~prime_genre)
```

According to the Figure \@ref(fig:data_plot2), for most kinds of apps, with the increase of application size, the average user evaluation increases with the increase of praise. Developers can gain higher user ratings by increasing the size of their apps.




# Yezi He

1. Most number of rating counts for which genre? (i.e., number of people who rated)

```{r}
num_rating_count <- dat %>%
  group_by(prime_genre) %>%
  summarise(count = sum(rating_count_tot))
num_rating_count_rank <- num_rating_count %>%
  rename(genre = "prime_genre") %>%
  arrange(-count) %>%
  head(7)
```

```{r numcount, fig.cap="Most number of rating counts for which genre"}            
ggplot(num_rating_count,
       aes(x = count,
           y = fct_reorder(prime_genre, count))) +
  geom_col() + 
  labs(x = "Number of rating counts",
       y = "Genre",
       title = "Most number of rating counts for which genre") 
```

```{r ranknumcount}
kable(num_rating_count_rank,
        caption = "The rank of rating counts for which genre") %>%
    kable_styling(bootstrap_options = 
                  c("striped", "condensed"), 
                  full_width = F,
                  position = "center") %>% 
    row_spec(c(1:3), 
             bold = T, 
             color = "white", 
             background = "steelblue")
```

It can be seen from Figure \@ref(fig:numcount) and Table \@ref(tab:ranknumcount) that the number of people who rated games is far more than the number of people who rated other genres. The top three are games, social networking and photo & video.

2. Rise/drop in rating since last update?

```{r}
rating_difference <- dat %>%
  mutate(rating_difference = user_rating_ver - user_rating) %>%
  group_by(prime_genre) %>%
  summarise(difference = mean(rating_difference))
rating_difference_rank <- rating_difference %>%
  rename(genre = "prime_genre") %>%
  arrange(difference) %>%
  head(7)
```

```{r ratingdifference, fig.cap="Rise/drop in rating since last update"}
ggplot(rating_difference,
       aes(x = difference,
           y = fct_reorder(prime_genre, difference))) +
  geom_col() + 
  labs(x = "Rating changes",
       y = "Genre",
       title = "Rise/drop in rating since last update")
```

```{r rankratingdifference}
kable(rating_difference_rank,
        caption = "The rank of rise/drop in rating since last update") %>%
    kable_styling(bootstrap_options = 
                  c("striped", "condensed"), 
                  full_width = F,
                  position = "center") %>% 
    row_spec(c(1:3), 
             bold = T, 
             color = "white", 
             background = "steelblue")
```

It can be seen from Figure \@ref(fig:ratingdifference) and Table \@ref(tab:rankratingdifference) that shopping apps have the fastest drop in ratings after last update. Finance and food & drink are followed in the ranking.

