---
title: "Assignment4-Group3"
author: "Group3"
date: "03/06/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Diyao Chen: 
1. Which genre are highest rated?
2. Which genre support most languages?
3. Which genre support most devices?

# Sen Wang: 
1. Genre-rating-price correlation?
2. Genre-rating-size correlation?

# Yezi He:
1. Most number of rating counts for which apps/genre? (i.e., number of people who rated)
2. Rise/drop in rating since last update?

# Ketan Kabu:
1. Development-Rating correlation?



```{r loading libraries, echo = FALSE, message = FALSE, warning = FALSE}
# Libraries

library(tidyverse)
library(readr)
library(kableExtra)
library(ggplot2)
```

# Introduction
Nowadays, more and more different type of App on the market. Some is for work, some is for entertainment,we know to know the feekback from the consumers.
In this section, we will analysis the realtionship between different type of app with user rating, language and support different devices.

```{r Read data source 1, fig.cap=" ", echo = FALSE, message = FALSE, warning=FALSE}
dat <- read_csv("C:/Users/61452/Desktop/Assign4-Group3/data/AppleStore.csv")
```

# Question1. Which genre are highest rated?
```{r q1, fig.cap="research for gener with rating ", echo = FALSE, message = FALSE, warning=FALSE}
genre_rating <- dat%>%
  group_by(prime_genre)%>%
  summarise(average_rating = mean(user_rating))%>%
  arrange(-average_rating)%>%
  unique()

 knitr::kable(genre_rating,booktabs = TRUE,
  caption = "Table1.Ranking of rating with different genre") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))%>%
  kable_styling(latex_options = "hold_position") 
  

Graph1<- genre_rating%>%
  ggplot(aes(x =reorder(prime_genre,-average_rating), y = average_rating))+
  geom_bar(stat = "identity")+
  ggtitle("Figure1.The ranking rate with different genre Apps")+
  theme(axis.text.x=element_text(angle = 90, hjust = 1))
print(Graph1)
```
As we can see from the table1 and the figure1, there are 23 different types of App in the research.


# Question2. Which genre support most language?
```{r q2, fig.cap="research for gener with language", echo = FALSE, message = FALSE, warning=FALSE}
gener_language <- dat%>%
  group_by(prime_genre)%>%
  summarise(average_language = mean(lang.num))%>%
  arrange(-average_language)


 knitr::kable(gener_language,booktabs = TRUE,
  caption = "Table2.Ranking of language with different genre") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))%>%
  kable_styling(latex_options = "hold_position") 
  

Graph2<- gener_language%>%
  ggplot(aes(x =reorder(prime_genre,-average_language), y = average_language))+
  geom_bar(stat = "identity")+
  ggtitle("Figure2.The ranking language with different genre Apps")+
  theme(axis.text.x=element_text(angle = 90, hjust = 1))
print(Graph2)
```



