---
title: "Assignment4-Group3"
author: "Group3"
date: "03/06/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Diyao Chen: 
1. Which genre are highest rated?
2. Which genre support most languages?
3. Which genre support most devices?

# Sen Wang: 
1. Genre-rating-price correlation?
2. Genre-rating-size correlation?

# Yezi He:
1. Most number of rating counts for which apps/genre? (i.e., number of people who rated)
2. Rise/drop in rating since last update?

# Ketan Kabu:
1. Development-Rating correlation?



```{r loading libraries, echo = FALSE, message = FALSE, warning = FALSE}
# Libraries

library(tidyverse)
library(readr)
library(kableExtra)
library(ggplot2)
```

# Introduction
In this section, we will analysis the realtionship between different type of app with user rating, language and support different devices.

```{r Read data source 1, fig.cap=" ", echo = FALSE, message = FALSE, warning=FALSE}
dat <- read_csv("C:/Users/61452/Desktop/Assign4-Group3/data/AppleStore.csv")
```